How Optimal is Word-Referent Identification Under Multimodal Uncertainty?

### 2018-11-05 Writeup/ms.tex
revisions

As a second analysis, we asked whether the observed variance in the
individual distribution was due to mere sampling errors or whether it
corresponded to a real between-subject variability. We simulated
individual responses from the posterior distribution whose parameters
were fit to the population as a whole (i.e., the descriptive posterior).
The resulting distribution is shown in Figure~\ref{fig:individual}. For
ease of comparison, the simulated distribution was superimposed to the
real distribution. We found that the real distribution had a standard
deviation of \(sd=\) 2.24 which was larger than that of the simulated
distribution (\(sd=\) 1.15), indicating that there was real
between-subject variation beyond sampling errors. This finding means
that the participants varied in terms of how they weighted modalities:
Compared to the predictions of the population-level model, some
participants relied more on the auditory modality, whereas others relied
more on the visual modality.

>>>>

As a second analysis, we asked whether the observed variance in the
individual distribution was due to mere sampling errors or whether it
corresponded to a real between-subject variability. We simulated
individual responses from the posterior distribution whose parameters
were fit to the population as a whole (i.e., the descriptive posterior).
The resulting distribution is shown in Figure~\ref{fig:individual}. For
ease of comparison, the simulated distribution was superimposed to the
real distribution. We found that the real distribution had a standard
deviation of \(sd=\) 2.24 which was larger than that of the simulated
distribution (\(sd=\) 1.14), indicating that there was real
between-subject variation beyond sampling errors. This finding means
that the participants varied in terms of how they weighted modalities:
Compared to the predictions of the population-level model, some
participants relied more on the auditory modality, whereas others relied
more on the visual modality.
